Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-22 WRITEUP/ms.tex
update error bar on r32

Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.41, where this error bar includes 
the uncertainties in absolute flux calibration.
This ratio is consistent with
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
% see DANNERBAUER09 intro
% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.

@@

%--------------------------------------------------------------------------
%                                Conclusions
%--------------------------------------------------------------------------
\section{Summary and Conclusions} \label{sec:sum}
We present PdBI \bco and CARMA \cco observations towards the
quadruply-imaged quasar RXJ1131 at $z_{\rm CO}$\ssim$0.654$, making this the first
resolved CO study at intermediate redshift.
Using the CO line intensities, we find a brightness temperature ratio of $r_{32}$\eq$0.78\,\pm\,0.41$
between the \bco and \cco lines,
consistent with thermalized excitation but also with the lower excitation seen in normal star-forming disks.
We also detect marginally resolved
2\,mm continuum emission underlying the \bco line
and resolved radio continuum emission at 5\,GHz in archival VLA data
in both the foreground lensing galaxy and RXJ1131.

>>>>

Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.37, where this error bar includes 
the uncertainties in absolute flux calibration.
This ratio is consistent with
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
% see DANNERBAUER09 intro
% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.

@@

%--------------------------------------------------------------------------
%                                Conclusions
%--------------------------------------------------------------------------
\section{Summary and Conclusions} \label{sec:sum}
We present PdBI \bco and CARMA \cco observations towards the
quadruply-imaged quasar RXJ1131 at $z_{\rm CO}$\ssim$0.654$, making this the first
resolved CO study at intermediate redshift.
Using the CO line intensities, we find a brightness temperature ratio of $r_{32}$\eq$0.78\,\pm\,0.37$
between the \bco and \cco lines,
consistent with thermalized excitation but also with the lower excitation seen in normal star-forming disks.
We also detect marginally resolved
2\,mm continuum emission underlying the \bco line
and resolved radio continuum emission at 5\,GHz in archival VLA data
in both the foreground lensing galaxy and RXJ1131.
